The Galactic Midplane is Not a Plane: Implications for dynamical analysis with {\em Gaia} data and beyond

### 2019-04-22 paper/ms.tex
Add Sun position, vcirc, fix errors

@@

The intuition behind the shape of Figure~\ref{fig:Jz_hist} is relatively
simple. Consider first the thick-disk orbit ({\em top} panel), where the
offset in $z$ is much less than $z_{\text{max}}$ of the orbit. The peaks in
the distribution correspond to the turning points of the orbit (or points of
maximum vertical amplitude), where $\v_z \sim 0$ and where the star spends
most of it orbit. This is why the distribution is peaked on these values. For
the thin-disk orbit ({\em bottom} panel), the offset in $z$ is comparable to
$z_{\text{max}}$. Now, there will be some points in the orbit where $v_z = 0$
and $z=0$ (in the observed, erroneous coordinate system). At these points, the
computed $J_z$ will vanish. The asymmetry and systematic offset then comes
about because of the constraint that $J_z \geg 0$.\footnote{This is similar to
arguments in cosmology for why gravity produces non-Gaussianity in the density
field, since the density cannot become negative but it can grow arbitrarily
large.}

>>>>

We assume the Sun is located at $(8.2, 0, 0)\,\kpc$. None of our orbit
calculations depend on the value of the LSR in this toy potential (though this
is important when using real data, since the conversion from heliocentric to
Galactocentric coordinates depends on the LSR). In this potential, we have
that the circular velocity $v_{\text{circ}}$ is $231\,\kms$ on the Solar
circle.

@@

The intuition behind the shape of Figure~\ref{fig:Jz_hist} is relatively
simple. Consider first the thick-disk orbit ({\em top} panel), where the
offset in $z$ is much less than $z_{\text{max}}$ of the orbit. The peaks in
the distribution correspond to the turning points of the orbit (or points of
maximum vertical amplitude), where $v_z \sim 0$ and where the star spends
most of it orbit. This is why the distribution is peaked on these values. For
the thin-disk orbit ({\em bottom} panel), the offset in $z$ is comparable to
$z_{\text{max}}$. Now, there will be some points in the orbit where $v_z = 0$
and $z=0$ (in the observed, erroneous coordinate system). At these points, the
computed $J_z$ will vanish. The asymmetry and systematic offset then comes
about because of the constraint that $J_z \geq 0$.\footnote{This is similar to
arguments in cosmology for why gravity produces non-Gaussianity in the density
field, since the density cannot become negative but it can grow arbitrarily
large.}
